The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-02 src/ms.tex
add new figure and text about new figure

@@

  While \astropy is used globally --- TODO figure with analytics --- our user
  community is underrepresented in non-English-speaking or -teaching countries
  and our maintainers and coordinators are fairly narrowly concentrated in the
  United States (US) and Europe.

>>>>

\begin{figure}[th!]
  \begin{centering}
    \includegraphics[width=\textwidth]{docu_analytics.pdf}
      \caption{
          The number of users who accessed the \astropypkg core package
          documentation in 2021, based on data from Google Analytics.
          The circle markers show the approximate locations of home institutions
          for \astropy voting members (green) and coordination committee members
          (red), demonstrating the over-representation of the United States and,
          less so, Europe given the global spread of \astropypkg users.
      }
      \label{fig:User-analytics-locations}
  \end{centering}
\end{figure}

@@

  While \astropy is used globally --- for example,
  Figure~\ref{fig:User-analytics-locations} shows the numnber of users per
  country who accessed the \astropypkg core package documentation in 2021 ---
  our user community is underrepresented in non-English-speaking or -teaching
  countries and our maintainers and coordinators are fairly narrowly
  concentrated in the United States (US) and Europe (see the circle markers on
  Figure~\ref{fig:User-analytics-locations}).
